### 2024-05-07 Text/Thesis/chapters/2_background.tex
doctoral qualification document

%Remote sensing is devoted to gathering information from the Earth’s surface at a distance~\citep{campbell2011introduction}, by means of electromagnetic energy or other mediums.

@@

%\section{Electromagnetic radiation}
\section{Remote Sensing} \label{sec:pr_obs}

@@

\setlength{\tabcolsep}{6.0pt}
\begin{table}[!htb]
\caption[Different bands in microwave remote sensing]{\label{tab:bands}Different bands in microwave remote sensing,~\citep{Moreira2013}.}
\centering
\begin{tabular}[t]{cccccc}
\toprule
 \textbf{Band} & \multicolumn{1}{c}{\textbf{Frequency} $\left[\text{GHz}\right]$} & \multicolumn{1}{c}{\textbf{Wavelength} $\left[\text{cm}\right]$} \\
\midrule
Ka & $\,25$--$40$ & $\phantom{-}0.75$--$1.2$ \\
Ku & $\,12$--$17.6$ & $\phantom{-}\,1.7$--$2.5$ \\
X  & $7.5$--$12$  & $2.5$--$4$   \\
C  & $ 3.75$--$7.5$ & $\phantom{-}4$--$8$   \\
S  & $2$--$3.75$   & $\phantom{-}\,8$--$15$    \\
L  & $1$--$2$   & $\phantom{-}15$--$30$   \\
P  & $0.3$--$1$ & $\phantom{-}\,30$--$100$  \\
\bottomrule
\end{tabular}
\end{table}
Table~\ref{tab:spacebornes} gives some examples of commonly used spaceborne SAR sensors, currently in operation. 
These include Radarsat-2 from the Canadian Space Agency (CSA), TerraSAR-X from the German Aerospace Center (DLR), ALOS PALSAR-2 from the Japan Aerospace Exploration Agency (JAXA), and Sentinel-1A/1B from the European Space Agency (ESA) (see Figure~\ref{fig:Sentinel-1}), as well as Gaofen-3 from the China National Space Administration (CNSA).
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{../../Images/PNG/ESA_radar.png}
    %\decoRule
    \caption[Sentinel-1 radar.]{Sentinel-1 radar, (source \href{https://www.esa.int/Applications/Observing_the_Earth/Copernicus/Sentinel-1/Changing_lands}{ESA}).}
    \label{fig:Sentinel-1}
\end{figure}

@@

In Figure~\ref{fig:speckle}, SAR images depict speckle, a characteristic of SAR data due to its coherent imaging process. 
The images distinguishes between fully developed speckle in homogeneous regions (Figure~\ref{fig:speckle} \ref{fig:s1}) and heterogeneous clutter in regions such as urban areas (Figure~\ref{fig:speckle} \ref{fig:s2}).
\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=.8\textwidth]{../../Images/PNG/Intensity_MG.png}
    \caption{Fully developed speckle (Homogeneous areas)}
    \label{fig:s1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{../../Images/PNG/urban_intensity.png}
    \caption{Heterogeneous clutter }
    \label{fig:s2}
  \end{subfigure}
  %\hfill
  %\begin{subfigure}[b]{0.3\textwidth}
    %\centering
    %\includegraphics[width=\textwidth]{example-image-c}
    %\caption{}
    %\label{fig: Third figure}
  %\end{subfigure}
  \caption{SAR image with speckle noise}
  \label{fig:speckle}
\end{figure}

\section{Dataset}
\subsection{Sentinel-1 SAR data processing}
The Sentinel-1 images were obtained from the Alaska Satellite Facility's (ASF) at \url{https://search.asf.alaska.edu/#/} and by the European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/}.

The downloaded SAR images were pre-processed using the Sentinel Application Platform (SNAP) Toolbox developed by ESA.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{../../Images/PNG/alaska1.png}
    %\decoRule
    \caption[Selection of area of interest]{Selection of area of interest.}
    \label{fig:alaska-area}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{../../Images/PNG/snap_1.png}
    %\decoRule
    \caption[SAR Images pre-processing  in the SNAP]{SAR Images pre-processing  in the SNAP.}
    \label{fig:alaska-area2}
\end{figure}

%\subsection*{Example math equations}
%-----------------------------------------------------------
%\begin{align*}
%L(\alpha,  \lambda|  \bm{x})&=\prod_{i=1}^n{f(x_i|\alpha, \lambda )}\\
                                 %&= \prod_{i=1}^n\left[\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\,x_i^{\alpha-1}\exp\left\{-\lambda x_i\right\}\right]\\
%&=\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n\prod_{i=1}^nx_i^{\alpha-1}\times \exp\left\{-\left(\lambda\sum_{i=1}^n x_i \right)\right\}
%\end{align*}
%%----------------------------------------------------------
%In Figure \ref{fig:undercatch}, in Eq, \eqref{eq:em}.
%\begin{align}
%\label{eq:em}
%\ell(\alpha, \lambda| \bm{x}) &=\log\left[\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n\prod_{i=1}^nx_i^{\alpha-1}\times \exp\left\{-\left(\lambda\sum_{i=1}^n x_i \right)\right\}\right]\nonumber\\
%&=\log\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n+\log\left[\prod_{i=1}^nx_i^{\alpha-1}\right]-\lambda\sum_{i=1}^nx_i\nonumber\\
%&=n\log\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)+(\alpha-1)\log\prod_{i=1}^nx_i-\lambda\sum_{i=1}^nx_i\nonumber\\
%&=n\log(\lambda^{\alpha})-n\log(\Gamma(\alpha))+(\alpha-1)\sum_{i=1}^n\log(x_i)-\lambda\sum_{i=1}^nx_i\nonumber\\
%&=n\alpha\log \lambda -n\log(\Gamma(\alpha)) +(\alpha-1)\sum_{i=1}^n\log(x_i)-\lambda\sum_{i=1}^nx_i.
	%\end{align}
%----------------------------------------------------------

%-------------------------------------------------------

%\begin{table}[h]
%\centering
%\caption{\label{tab1}Comparação de tempos. }
%\begin{tabular}{l c c }
%\toprule[1pt] \textbf{Amostra (N)} \ \ \  \ \ \  & \textbf{Tempo de Execução (C)}\ \ \ \ \ \ \  &\textbf{Tempo de Execução (Ox)} \\\midrule[0.5pt]
%$20$ & 7.6810 s  &  5.01 s \\
%$30$ & 9.6260 s     & 5.34 s \\
%$50$ &  10.0310 s & 5.99 s \\
%$100$ & 15.5420 s & 8.07 s \\
%$200$ & 20.5860 s & 9.64 s \\
%$500$ & 29.0890  s & 15.12 s \\
%\bottomrule[1pt]
%\end{tabular}
%\caption[Precipitation datasets]{List of datasets used in the analysis of daily precipitation uncertainty carried over i}\label{tab:1}
%\end{table}
%------------------------------------------------------

%\begin{table}[]
%\centering
%\begin{tabular}{@{}llll@{}}
%\toprule
%Dataset name & Period & Spatial res. & Data source \\ \midrule
%E-OBS        & 2000--2016 & \ang{0.25}                            & Station data \\
%EURO4M-APGD  & 2000--2008 & \SI{5}{\kilo\metre}                   & Station data \\
%HMR          & 2000--2013 & \SI{5.5}{\kilo\metre}                 & Reanalysis \\
%ARCIS        & 2000--2015 & \textasciitilde{} \SI{5}{\kilo\metre} & Station data \\
%CHIRPS       & 2000--2016 & \ang{0.05}                            & Station data + satellite \\
%CPC          & 2000--2016 & \ang{0.5}                             & Station data \\
%CMORPH       & 2000--2016 & \ang{0.25}                            & Satellite \\
%PERSIANN-CDR & 2000--2016 & \ang{0.25}                            & Satellite \\ \bottomrule
%\end{tabular}
%\caption[ Italy]{List of datasets used in the analysis of daily precipitation uncertainty  references.}\label{tab:2}
%\end{table}

>>>>

@@

\section{Remote Sensing} \label{sec:pr_obs}

@@

\setlength{\tabcolsep}{6.0pt}
\begin{table}[!htb]
\caption[Different bands in microwave remote sensing]{\label{tab:bands}Different bands in microwave remote sensing,~\citep{Moreira2013}.}
\centering
\begin{tabular}[t]{cccccc}
\toprule
 \textbf{Band} & \multicolumn{1}{c}{\textbf{Frequency} $\left[\text{GHz}\right]$} & \multicolumn{1}{c}{\textbf{Wavelength} $\left[\text{cm}\right]$} \\
\midrule
Ka & $\,25$--$40$ & $\phantom{-}0.75$--$1.2$ \\
Ku & $\,12$--$17.6$ & $\phantom{-}\,1.7$--$2.5$ \\
X  & $7.5$--$12$  & $2.5$--$4$   \\
C  & $ 3.75$--$7.5$ & $\phantom{-}4$--$8$   \\
S  & $2$--$3.75$   & $\phantom{-}\,8$--$15$    \\
L  & $1$--$2$   & $\phantom{-}15$--$30$   \\
P  & $0.3$--$1$ & $\phantom{-}\,30$--$100$  \\
\bottomrule
\end{tabular}
\end{table}
Table~\ref{tab:spacebornes} gives some examples of commonly used spaceborne SAR sensors, currently in operation. 
These include Radarsat-2 from the Canadian Space Agency (CSA), TerraSAR-X from the German Aerospace Center (DLR), ALOS PALSAR-2 from the Japan Aerospace Exploration Agency (JAXA), and Sentinel-1A/1B from the European Space Agency (ESA) (see Figure~\ref{fig:Sentinel-1n}), as well as Gaofen-3 from the China National Space Administration (CNSA).
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{../../Images/PNG/ESA_radar.png}
    %\decoRule
    \caption[Sentinel-1 radar.]{Sentinel-1 radar, (source \href{https://www.esa.int/Applications/Observing_the_Earth/Copernicus/Sentinel-1/Changing_lands}{ESA}).}
    \label{fig:Sentinel-1n}
\end{figure}

@@

In Figure~\ref{fig:speckle}, SAR images depict speckle, a characteristic of SAR data due to its coherent imaging process. 
The images distinguishes between fully developed speckle in homogeneous regions (Figure~\ref{fig:speckle} \ref{fig:s1}) and heterogeneous clutter in regions such as urban areas (Figure~\ref{fig:speckle} \ref{fig:s2}).
\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=.8\textwidth]{../../Images/PNG/Intensity_MG.png}
    \caption{Fully developed speckle (Homogeneous areas)}
    \label{fig:s1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{../../Images/PNG/urban_intensity.png}
    \caption{Heterogeneous clutter }
    \label{fig:s2}
  \end{subfigure}
  \caption{SAR image with speckle noise}
  \label{fig:speckle}
\end{figure}

\section{Dataset}
\subsection{Sentinel-1 SAR data processing}
The Sentinel-1 images were obtained from the Alaska Satellite Facility (ASF) at \url{https://search.asf.alaska.edu/#/} and by the European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (see Figure~\ref{fig:alaska-area1}).

The SAR images downloaded were pre-processed using the Sentinel Application Platform (SNAP) Toolbox developed by ESA (see Figure~\ref{fig:alaska-areaf}).

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{../../Images/PNG/alaska1.png}
    %\decoRule
    \caption[Selection of area of interest]{Selection of area of interest.}
    \label{fig:alaska-area1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{../../Images/PNG/snap_1.png}
    %\decoRule
    \caption[SAR Images pre-processing  in the SNAP]{SAR Images pre-processing  in SNAP.}
    \label{fig:alaska-areaf}
\end{figure}

### 2024-05-07 Text/Thesis/chapters/3_methods.tex
doctoral qualification document

\subsection{The Proposed Test Based on Coefficient of Variation and a
Robust
Alternative}\label{the-proposed-test-based-on-coefficient-of-variation-and-a-robust-alternative}

>>>>

\subsection[The Proposed Test Based on CV and a Robust Alternative]{The Proposed Test Based on Coefficient of Variation and a
Robust
Alternative}\label{the-proposed-test-based-on-coefficient-of-variation-and-a-robust-alternative}
